Data Management \\ and LSST Special Programs

### 2021-11-27 DMTN-065.tex
removed references to DM-12574

\textbf{Shorter Exposures.} The camera constraint on the minimum supported exposure time is currently 1 second (stretch goal 0.1 seconds). The minimum exposure time for an image to be successfully reduced with Instrument Signature Removal (ISR) is under consideration (see JIRA ticket DM-12574). Assuming that 1 second exposure can be reduced and calibrated, its detected point sources will span a dynamic range of $r \approx 12.9$ -- $21.0$ magnitudes. A template image built on $15$ second exposures will saturate at $r \approx 15.8$, but this still leaves stars between $15.8$--$21.0$ magnitudes to be used in the PSF-matching (and all other filters have a similarly large overlap). However, in order for an image to be successfully PSF-matched to the template, the PSF must be well formed (no speckle pattern), and have a spatial variance that the pipeline is capable of modeling (be smoothly varying on some minimal scale). As a simple demonstration, Figure \ref{fig:expt} shows that perhaps exposure times shorter than $2$ seconds do not have a well-formed PSF (using the centroid of a 2D Gaussian fit as a proxy for "well-formed"). The minimum exposure time for an image to be successfully processed by the Difference Imaging Analysis (DIA) pipeline is currently under consideration (see JIRA ticket DM-12574).

@@

\textbf{Longer Exposures.} There is no maximum exposure time specified for an LSST image. Given that the template image will be a stack of at least a year or two of data, processing a $5$--$10$ times deeper single image through the difference imaging pipeline should be fine. However, a $2\times150$ second exposure would saturate at $r \approx 18.3$, and cosmic-ray rejection completeness might suffer (unknown), which could impact the quality of a difference image and the detected sources. Additionally, any system qualities that vary on short (but $>30$ second) timescales could inhibit photometric calibration (e.g., tracking). A potential maximum exposure time from a processing perspective is currently under consideration (see JIRA ticket DM-12574).

@@

There may be a couple of issues encountered with Alerts from many consecutive visits of Deep Drilling fields. One is that, since the Alert contains the full record of all associated {\tt DIASources} from the past 12 months (\citeds{LSE-163}), for a Deep Drilling Field with significantly more visits over the year, the size of the Alert might become prohibitively large (TBD). Another is that the self-consistency of the \texttt{DIAObjects} catalog may suffer during consecutive visits of a single field. For example, the processing for image $2$ of a sequence would begin when the processing for image $1$ is only halfway complete. Any new {\tt DIASource} in image $1$ that cannot be associated (by coordinate) with an existing {\tt DIAObject} becomes a new {\tt DIAObject}. When this source is again detected in image $2$, another new {\tt DIAObject} would be created if the catalog has not yet been updated. The best solution might be to flag {\tt Alerts} which may suffer from incomplete {\tt DIASource}--{\tt DIAObject} associations (see JIRA ticket DM-12574).

>>>>

\textbf{Shorter Exposures.} The camera constraint on the minimum supported exposure time is currently 1 second (stretch goal 0.1 seconds; LSR-REQ-0111 in \citeds{LSE-29}).
As with all requirements, this one would be verified during commissioning.
Assuming that 1 second exposure can be reduced and calibrated, its detected point sources will span a dynamic range of $r \approx 12.9$ -- $21.0$ magnitudes.
A template image built on $15$ second exposures will saturate at $r \approx 15.8$, but this still leaves stars between $15.8$--$21.0$ magnitudes to be used in the PSF-matching (and all other filters have a similarly large overlap).
However, in order for an image to be successfully PSF-matched to the template, the PSF must be well formed (no speckle pattern), and have a spatial variance that the pipeline is capable of modeling (be smoothly varying on some minimal scale).
As a simple demonstration, Figure \ref{fig:expt} shows that perhaps exposure times shorter than $2$ seconds do not have a well-formed PSF (using the centroid of a 2D Gaussian fit as a proxy for "well-formed").

@@

\textbf{Longer Exposures.} There is no maximum exposure time specified for an LSST image.
Given that the template image will be a stack of at least a year or two of data, processing a $5$--$10$ times deeper single image through the difference imaging pipeline should be fine.
However, a $2\times150$ second exposure would saturate at $r \approx 18.3$, and cosmic-ray rejection completeness might suffer (unknown), which could impact the quality of a difference image and the detected sources.
Additionally, any system qualities that vary on short (but $>30$ second) timescales could inhibit photometric calibration (e.g., tracking).

@@

There may be a couple of issues encountered with Alerts from many consecutive visits of Deep Drilling fields. One is that, since the Alert contains the full record of all associated {\tt DIASources} from the past 12 months (\citeds{LSE-163}), for a Deep Drilling Field with significantly more visits over the year, the size of the Alert might become prohibitively large (TBD). Another is that the self-consistency of the \texttt{DIAObjects} catalog may suffer during consecutive visits of a single field. For example, the processing for image $2$ of a sequence would begin when the processing for image $1$ is only halfway complete. Any new {\tt DIASource} in image $1$ that cannot be associated (by coordinate) with an existing {\tt DIAObject} becomes a new {\tt DIAObject}. When this source is again detected in image $2$, another new {\tt DIAObject} would be created if the catalog has not yet been updated.
